Active Object Search with a Mobile Device for the Visually Impaired

### 2018-11-23 paper.tex
Minor typo changes

Here we focus in particular on the implementation of the control module $K$. Two important points are considered in the design of the controller. Firstly, $K$ must be scenario-agnostic, meaning that objects could be placed in different places, unknown a priori. Secondly, the controller must be robust enough to handle incorrect interpretations by the human of the instructions $u$. This risk can be mitigated by the use of clear and simple instructions that help $u^*$ follow as close as possible $u$. The implementation of this controller is discussed in detailed next.

@@

\noindent Our active search system guides the user by generating a set of waypoints that need to observed by the camera, tracing a path that will eventually lead to the target object. Note that the actual location of the latter is {\em unknown}, meaning that the system will guide the user towards the most likely location where to find the object, based on its internal knowledge of spatial relations between objects (e.g. a computer is more likely to be above than below a desk). This path is generated one waypoint at a time and is updated with every new object observation captured by the camera, or after a re-orientation of the latter beyond a certain angle. We tackle the problem using an MDP, the design and implementation of which are discussed in the following sub-sections. %For this initial design, the system only works in the pan and tilt dimension and the depth dimension will be added after successful testing of this version of the guidance system.
 %The guidance system is built into an Android app and uses Android's ARCore API to track the device's pose. 
%\subsection{Environment Model}\label{sec:env-design}

>>>>

Here we focus in particular on the implementation of the control module $K$. Two important points are considered in the design of the controller. Firstly, $K$ must be scenario-agnostic, meaning that objects could be placed in different places, unknown a priori. Secondly, the controller must be robust enough to handle incorrect interpretations by the human of the instructions $u$. This risk can be mitigated by the use of clear and simple instructions that helps $u$ track $u^*$ as closely as possible. The implementation of this controller is discussed in detail next.

@@

\noindent Our active search system guides the user by generating a set of waypoints that need to observed by the camera, tracing a path that will eventually lead to the target object. Note that the actual location of the latter is {\em unknown}, meaning that the system will guide the user towards the most likely location where to find the object, based on its internal knowledge of spatial relations between objects (e.g.\ a computer is more likely to be above than below a desk). This path is generated one waypoint at a time and is updated with every new object observation captured by the camera, or after a re-orientation of the latter beyond a certain angle. We tackle the problem using an MDP, the design and implementation of which are discussed in the following sub-sections. %For this initial design, the system only works in the pan and tilt dimension and the depth dimension will be added after successful testing of this version of the guidance system.
 %The guidance system is built into an Android app and uses Android's ARCore API to track the device's pose. 
%\subsection{Environment Model}\label{sec:env-design}
